Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-24 paper.tex
FastR provenance

While the job is executing, input URIs are translated to their actual values,
the execution environment is set up by the \textit{Tool} and the \textit{Tool}
command is executed by the \textit{Interface}. When the \textit{Interface}
returns the results, the
output data is validated and translated to URI format.

@@

        \subsection{Debugging and Provenance}
    \section{OpenMOLE}
        \subsection{summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

While the job is executing, input URIs are translated to their actual path/values,
the execution environment is set up by the \textit{Tool} and the \textit{Tool}
command is executed by the \textit{Interface}. When the \textit{Interface}
returns the results, the
output data is validated and translated to URI format.

@@

        \subsection{Debugging and Provenance}
        In FastR, a provenance document is generated for each resulting file
generated in the Prov-N format. Data recorded in the provenance documents include \textit{Tool}
versions, input/output paths/values and their respective checksums, start and
end time of execution for each \textit{job}, stdout and stderr logs, the end
status and the complete environment description.

    Similarly to Nipype, the FastR network can be visualized using graphviz.

    \section{OpenMOLE}
        \subsection{summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
